Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-02 appendix.tex
Address comments on figure 5

@@

% -----------------------------------------------------------------------------
\subsection{Section 6.3 - Figure 14}
\label{apndx:fig14}

% -----------------------------------------------------------------------------
\subsection{Section 6.3 - Figure 15}
\label{apndx:fig15}

% -----------------------------------------------------------------------------
\subsection{Section 6.3 - Figure 16}
\label{apndx:fig16}

% -----------------------------------------------------------------------------
\subsection{Section 6.3 - Figure 17}
\label{apndx:fig17}

>>>>

\begin{description}[align=left]
    \item [Section 5.1 -- Figure 3] \url{}
    \item [Section 5.1 -- Figure 4] \url{}
    \item [Section 5.1 -- Figure 5] \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/figure_5}
    \item [Section 5.1 -- Figure 6] \url{}
    \item [Section 5.2 -- Figure 7] \url{}
    \item [Section 5.2 -- Figure 8] \url{}
    \item [Section 5.3 -- Figure 9] \url{}
    \item [Section 6.3 -- Figure 14] \url{}
    \item [Section 6.3 -- Figure 15] \url{}
    \item [Section 6.3 -- Figure 16] \url{}
    \item [Section 6.3 -- Figure 17] \url{}
    \item [Section 6.3 -- Figure 18] \url{}
    \item [Section 6.3 -- Figure 19] \url{}
    \item [Section 6.3 -- Figure 20] \url{}
    \item [Section 6.3 -- Figure 21] \url{}
\end{description}

@@

% -----------------------------------------------------------------------------
\subsection{Section 6.3 - Figure 7}
\label{apndx:fig9}

\begin{itemize}
    \item Raw data: \url{https://github.com/ATLAS-Titan/misc/tree/master/atlas-paper-experiments/data}
     \item Processed data: \url{ https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/NGE/data.csv} 
    \item Raw data processing: 
    	\begin{itemize}
    		\item Download \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/NGE/dataAnalysis.py}
    		\item Download \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/NGE/script.py}
    		\item Follow instructions at: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/wiki/How-to-extract-data-from-the-sandbox}
   	\end{itemize}
    \item Plotting code: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/NGE/plot.gnu}
\end{itemize}

Replicability: Follow instructions at the following link: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/wiki/How-to-reproduce-experiments-on-TITAN} to prepare the environment on Titan.
Launch:
\begin{itemize}
\item python dispatcher.py 250 250 120 etc/input_100 to replicate experiments with 250 nodes;
\item python dispatcher.py 500 500 120 etc/input_100 to replicate experiments with 500 nodes;
\item python dispatcher.py 1000 1000 120 etc/input_100 to replicate experiments with 1000 nodes;
\item python dispatcher.py 2000 2000 120 etc/input_100 to replicate experiments with 2000 nodes.
\end{itemize}

% -----------------------------------------------------------------------------
\subsection{Section 6.3 - Figure 8}
\label{apndx:fig10}
\begin{itemize}
    \item Raw data: \url{https://github.com/ATLAS-Titan/misc/tree/master/atlas-paper-experiments/weak2}
     \item Processed data: \url{ https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/NGE/weak2.csv} 
    \item Raw data processing: 
    	\begin{itemize}
    		\item Download \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/NGE/dataAnalysis.py}
    		\item Download \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/NGE/script.py}
    		\item Follow instructions at: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/wiki/How-to-extract-data-from-the-sandbox}
   	\end{itemize}
    \item Plotting code: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/NGE/plot.gnu}
\end{itemize}

Replicability: Follow instructions at the following link: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/wiki/How-to-reproduce-experiments-on-TITAN} to prepare the environment on Titan.
Launch:
\begin{itemize}
\item python dispatcher.py 256 1280 256 180 etc/input_16 to replicate experiments with 256 nodes;
\item python dispatcher.py 512 2560 512 180 etc/input_16 to replicate experiments with 512 nodes;
\item python dispatcher.py 1024 5120 180 etc/input_16 to replicate experiments with 1024 nodes;
\item python dispatcher.py 2048 10240 180 etc/input_16 to replicate experiments with 2048 nodes.
\end{itemize}

% -----------------------------------------------------------------------------
\subsection{Section 6.3 - Figure 9}
\label{apndx:fig16}

\label{apndx:fig10}
\begin{itemize}
    \item Raw data: \url{https://github.com/ATLAS-Titan/misc/tree/master/atlas-paper-experiments/strong}
     \item Processed data: \url{ https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/NGE/strong.csv} 
    \item Raw data processing: 
    	\begin{itemize}
    		\item Download \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/NGE/dataAnalysis.py}
    		\item Download \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/NGE/script.py}
    		\item Follow instructions at: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/wiki/How-to-extract-data-from-the-sandbox}
   	\end{itemize}
    \item Plotting code: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/NGE/plot.gnu}
\end{itemize}

Replicability: Follow instructions at the following link: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/wiki/How-to-reproduce-experiments-on-TITAN} to prepare the environment on Titan.
Launch:
\begin{itemize}
\item python dispatcher.py 256  2048 256 180 etc/input_16 to replicate experiments with 256 nodes;
\item python dispatcher.py 512 2048 512 180 etc/input_16 to replicate experiments with 512 nodes;
\item python dispatcher.py 1024 2048 180 etc/input_16 to replicate experiments with 1024 nodes;
\item python dispatcher.py 2048 2048 180 etc/input_16 to replicate experiments with 2048 nodes.
\end{itemize}

% -----------------------------------------------------------------------------
